Block bootstrap consistency\\under weak assumptions

### 2016-06-10 Paper.tex
[#26] Relabel lemmas and theorems in LaTeX source
Closes #26.

\begin{lem}\label{L1}
  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
  $J_n$ so that $\sum_{i=1}^{J_n-1} M_{ni} < n \leq \sum_{i=1}^{J_n} M_{ni} $
  Then
  \begin{enumerate}
  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
    for any positive $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$ and $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$, and
  \item $\sum_{i=1}^{J_n} M_{ni}^2 = O_p(n/p_n)$.
  \end{enumerate}
\end{lem}

@@

  The proof of part 4 is the same as part 2, making the obvious
  substitutions.
  Using the same argument as in part 2 of this Lemma, it suffices to
  prove that
  $\sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor} M_{ni}^2 =
  O_p(n/p_n)$ where $C$ is an arbitrary constant greater than 1.  The
  LLN implies that
  \begin{equation*}
    \tfrac{1}{C n p_n} \sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor}
    M_{ni}^2 = \tfrac{2 - p_n}{p_n^2} + o_p(\tfrac{2 - p_n}{p_n^2})
  \end{equation*}
  and the result follows immediately.
\end{proof}

>>>>

\begin{lem}\label{L1}
  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
  $J_n$ so that $\sum_{i=1}^{J_n-1} M_{ni} < n \leq \sum_{i=1}^{J_n} M_{ni} $
  Then
  \begin{enumerate}
  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
    for any positive $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$ and $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$, and
  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
  \end{enumerate}
\end{lem}

@@

  The proof of part 4 is the same as part 2, making the obvious
  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
  probability by part 2.
\end{proof}
